Energy Regulation for Biologically-inspired Robotics

### 2021-09-19 latex/nserc/contributions.tex
Major edits of contributions.

\subsection*{Part II: Most Significant Contributions to Research \& Development}
\textit{Describe your role in research, clarify your contribution, provide
    details on significance of tech report, indicate collaborations, discuss
relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
My contribution was substantial: I produced the theoretical and simulation
results (with lots of advice from my supervisor, Fady Alajaji), and then I wrote
the report in its entirety.
%In the report, I summarized the existing theory on the
%\textit{information bottleneck} (IB) and its variant, the \textit{deterministic
%information bottleneck} (DIB), which are tools from information theory that
%have been touted as a rigorous foundation for Deep Neural Networks. 
%The DIB in particular is useful for clustering data.
%Its equations are defined using an information-theoretic concept called
%``Shannon's Mutual Information" (SMI).
%In this report, Alajaji suggested we extend the equations by using a more
%general concept called ``R\'{e}nyi's Mutual Information" to get the aptly-named
%\textit{R\'{e}nyi's deterministic information bottleneck} (RDIB).
%I compared the efficacy of the DIB and RDIB for clustering data, and we found
%that the RDIB is more robust when the probability distribution of the data model 
%does not match the true distirbution which generated the data.
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019. 
It also motivated further research, which was published in [1].

@@

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
\textit{Describe scientific and engineering abilities you gained in past
    research experience, including projects, honours thesis, coop reports. If
    you have work experience, discuss relevance of that to your proposed field
of study and what benefits you gained.}
The following list outlines the scientific and engineering abilities I gained in
my research and professional roles.
\begin{itemize}
    \item \textbf{MASc Research, University of Toronto, 2018 -- 2021}
        TODO.
        Research skills: time management, critical thinking, coming up with
        well-formulated research question, tenacity and creativity
        (always ``attacking" the problem from multiple directions), dedication
        to solving a complex problem, explaining
        my work both orally and in writing, presentation skills, 
        literature reviews and how to read papers
        Engineering skills: nonlinear control techniques, implementation of
        control systems on hardware

    \item \textbf{Radar Developer, 2018}
        TODO:
        Managing a software project, implementing software for a hardware
        system, validating documentation (i.e. never trust it blindly).

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}
        TODO:
        First time doing a research project. Collaborating with fellow
        researchers. Coming up with an application for existing research. Basic
        literature review skills, report writing. Code optimization (turning
        equations into matrix form for speed, parallelization, C++ vs MATLAB),
        creating a GUI for users.

    \item \textbf{Software Developer, Neptec Technologies Crop, 2016 -- 2017}
        My experience at Neptec was incredibly beneficial.
        I worked on several embedded software projects, including a control
        systems project. The exposure to various areas of electrical and
        computer engineering is what convinced me to pursue research in the
        first place.
        I learned to work on large software projects, where multiple people work
        together on the same topic.
        I also became extremely proficient at software development, a skill
        which has served me well in my research experiments on physical robots.

@@

\subsubsection*{Relevant Activities}
\textit{Describe professional, academic, extracurricular activities that
    demonstrate communication, interpersonal and leadership skills, e.g.
    teaching, mentoring, managing projects, volunteer work, committee work,
participation in organizations and clubs, or work experience}.

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles, along with a summary
of what I learned.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund (LMF) -- the social
    committee for Massey College, a graduate residence at the University of
    Toronto.
    In managing 13 orientation events for 150 members of the college, I have
    learned to explicitly communicate my needs with others, and to ask pointed
    questions to understand their needs.

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course I teach improves my communication skills, and I've learned
    many ways of making course material fun and engaging.
    I focus most on student participation by finding making them feel
    comfortable asking questions.

\item \textbf{Jiu-Jitsu Instructor, 2019 -- Present}. 
    I am an instructor at the University of Toronto Jiu-Jitsu club. I teach
    people martial arts while fostering a safe, friendly atmosphere that
    encourages learning through action.
    This role has refined my communication and interpersonal skills:
    it has taught me to create learning plans for my students;
    break down difficult concepts into manageable chunks; 
    and to reward mistakes, because the best way to learn is to try, fail, and
    always try again.

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team, 2017 -- 2018}. 
    In this role, I taught C++ and information theory to the team’s software
    developers. I learned project management skills by organizing
    the satellite codebase, and I took on a supportive role for my peers rather
    than writing the software myself.

@@

I take pride in my teaching, communication, and leadership abilities.
Obtaining an NSERC scholarship will provide me with the financial liberty to
participate in more volunteer roles, where I can better myself while giving back to my
community.

>>>>

\subsection*{Part II: Most Significant Contributions to Research \& Development}
%\textit{Describe your role in research, clarify your contribution, provide
%    details on significance of tech report, indicate collaborations, discuss
%relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
My contribution was substantial: I produced the theoretical and simulation
results (with an abundance of advice from my supervisor, Fady Alajaji), and I
wrote the report in its entirety.
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019, and it motivated further research [1].

@@

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
%\textit{Describe scientific and engineering abilities you gained in past
%    research experience, including projects, honours thesis, coop reports. If
%    you have work experience, discuss relevance of that to your proposed field
%of study and what benefits you gained.}
The following list outlines the scientific and engineering abilities I gained in
my research and professional roles.
\begin{itemize}
    \item \textbf{MASc Research, University of Toronto, 2018 -- 2021}.
        In my master's degree, I learned several important research skills:
        my supervisor taught me to correctly formulate research questions;
        I learned the tenacity and dedication required to solve a
        complex problem; I developed my creativity by attacking problems from
        multiple directions; I learned to read papers, perform a literature
        review, think critically about the literature, and apply existing
        results to my research; I improved my time management skills, practiced
        explaining my work (both orally and in writing), and improved my
        presentation skills for the thesis defense; and I learned to write
        research papers and a thesis, which are important for communicating my
        work to the engineering community.
        I also learned several engineering skills, including advanced control
        techniques; simulation of physical systems in MATLAB; and implementation
        of control systems in hardware.

    \item \textbf{Radar Developer, University of Toronto, 2018}.
        I wrote software for a radar device as part of a group project in one of
        my graduate courses.
        This project taught me several engineering skills.
        First, I improved my project management skills by keeping our group
        meetings organized, and by separating the tasks in such a way
        that everyone was learning something from the project.
        I learned to read hardware documentation and to wire a device from
        schematics.
        I wrote networking code in Python to interface with the
        device, and validatet the hardware's capabilities for myself by
        creating appropriate testing environments. 
        All these skills will be beneficial for my PhD research when I build a
        robot.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}.
        For my undergraduate thesis, I worked with my peers to find an
        application for existing theoretical results. 
        During this project I also learned to perform a basic literature review,
        and to manage deadlines with a supervisor.
        In terms of engineering skills, I learned to write reports in LaTeX
        and my thesis group worked together on code optimization: we learned to
        convert equations into matrix form to take advantage of hardware
        optimization; we parallelized our code so our algorithm would run faster
        through multithreading; we ported MATLAB code to C++ to achieve even
        faster results; and we created a GUI so we could test our code quickly
        and easily.

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career, as it is what drove
        me to pursue research in robotics.
        Working at Neptec exposed me to several areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        I loved this project, and I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        I also learned to work on large software projects, where multiple people work
        together on the same topic; 
        and I became extremely proficient at software development, a skill which
        has served me well in my research experiments on physical robots.

@@

\subsubsection*{Relevant Activities}
%\textit{Describe professional, academic, extracurricular activities that
%    demonstrate communication, interpersonal and leadership skills, e.g.
%    teaching, mentoring, managing projects, volunteer work, committee work,
%participation in organizations and clubs, or work experience}.

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund, which is the events
    committee for Massey College (an interdisciplinary college at the University
    of Toronto).
    I have already organized 13 events for members of the college, and will
    continue to organize biweekly events throughout the year.
    This role has taught me the logistics and leadership skills required to
    manage large events for 150 people.
    I have also learned to make events accessible to everyone by asking
    questions so I can understand the needs of all attendees.

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course I teach improves my communication skills, and each tutorial gives
    me the opportunity to make the course material more fun and engaging.
    I focus most on attaining high levels of student participation by being
    kind and non-judgemental, which makes students feel
    comfortable enough to ask whatever question crosses their mind.

\item \textbf{Jiu-Jitsu Instructor, 2019 -- Present}. 
    I am an instructor at the University of Toronto Jiu-Jitsu club. I teach
    martial arts while fostering a safe, friendly atmosphere that
    encourages learning through action.
    This role has refined my communication and interpersonal skills:
    it has taught me to create learning plans for my students;
    break down difficult concepts into manageable chunks; 
    and to reward students for trying their best, even if they make a mistake.

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team, 2017 -- 2018}. 
    In this role, I taught C++ and information theory to the team’s software
    developers. I learned project management skills by organizing
    the satellite codebase and handling code reviews, and I took on a supportive
    and mentorship role for my peers rather than writing software myself.

@@

I take pride in my teaching, communication, and leadership abilities, yet I
remain aware that these can always be improved.
Obtaining an NSERC scholarship will provide me with the financial liberty to
participate in more volunteer roles, where I can better myself while giving back to my
community.

### 2021-09-19 latex/nserc/proposal.tex
Major edits of contributions.

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to robots which can walk or drive, 
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through trees.

>>>>

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to mobile animal-like robots,
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through trees.
